### 2024-11-28 README.Rmd
reorganize sim_metrics for matrices

To quantify how good and how intense the texts are, we can compare them to the embeddings for "good" and "intense" using `get_similarities()`. Note that this step requires only a dataframe,  tibble, or embeddings object with numeric columns; the embeddings can come from any source.

```{r}
good_vec <- predict(glove_twitter_25d, "good")
intense_vec <- predict(glove_twitter_25d, "intense")
valence_quantified <- valence_embeddings_df |> 
	get_similarities(
		dim_1:dim_25, 
		list(
			good = good_vec, 
			intense = intense_vec
			)
		)
valence_quantified
```
### Example Quanteda Workflow

>>>>

To quantify how good and how intense the texts are, we can compare them to the embeddings for "good" and "intense" using `get_sims()`. Note that this step requires only a dataframe,  tibble, or embeddings object with numeric columns; the embeddings can come from any source.

```{r}
good_vec <- predict(glove_twitter_25d, "good")
intense_vec <- predict(glove_twitter_25d, "intense")
valence_quantified <- valence_embeddings_df |> 
	get_sims(
		dim_1:dim_25, 
		list(
			good = good_vec, 
			intense = intense_vec
			)
		)
valence_quantified
```
### Example Quanteda Workflow
